\documentclass[pdf]{beamer}
\mode<presentation>{\usetheme{Warsaw}\usecolortheme{crane}}
\usepackage{centernot}

%% preamble
\title{UNIX Weapons School, Week 0}
\subtitle{{\it Lasciate ogni speranza, voi ch'entrate!}}
\author{Nick Black for the\\
Georgia Institute of Technology}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Goals}

\begin{itemize}
\item Train formidably competent systems programmers.
\item Ensure GT continues to graduate world-class hackers.
\item Provide a fast-paced challenge for talented, driven students. 
\end{itemize}
\end{frame}

\begin{frame}{Assumptions}
\begin{itemize}
\item You are not required to take this class.
\uncover<2->{
\begin{itemize}
\item This assumption is also an answer to most complaints.
\item Hopefully you represent a self-selection of the elite.
\end{itemize}
}
\item You are dexterous with C.
\uncover<3->{
\begin{itemize}
\item You ought be able to pump out working C pretty quickly...
\item ... and be able to recognize any C construct.
\item A copy of {\it The C Programming Language} is recommended.
\end{itemize}
}
\item You have a 64-bit x86 Linux box easily available.
\uncover<4->{
\begin{itemize}
\item I can't {\it require} you to install Linux, but...
\item Why aren't you running open source?
\item We will regularly refer to and modify GNU/Linux source code.
\end{itemize}
}
\end{itemize}
\end{frame}

\begin{frame}{Relation to CoC I}
UWS relies upon and extends:
\begin{itemize}
\item CS2130 (Bill Leahy) -- C-based weed-out
\item CS35xx (Dr. STAFF) -- Algorithms
\item CS325x (Dr. STAFF) -- Networking
\end{itemize}
UWS borrows material from:
\begin{itemize}
\item CS6230 (Richard Vuduc) -- HPC Tools and Methods
\item CS6290 (Hyesoon Kim / Milos Prvulovic) -- Comp Arch
\item CS6251 (Santosh Pande) -- Compiler Design
\item Whatever Tom Conte's teaching at the moment
\end{itemize}
\end{frame}

\begin{frame}{Relation to CoC II}
but... \\
\emph{UWS focuses on {\it use} of these theories to produce high-performance,
robust, {\it practical} software solutions.}\linebreak \\
e.g.: \\
You will not gain experience implementing SSA (single static
assignment, which if you don't know now, you'll know later), but you will
understand the space of optimizations an SSA-driven compiler can effect on your
code.\linebreak \\
{\bf UWS will involve writing \~{}10,000 lines of code in 9 weeks.}\linebreak \\
This is Sparta, young friends. Feel free to leave.
\end{frame}

\begin{frame}{Grading function $G(p)$}
\begin{itemize}
\item $|S|$ students with four projects score $\{P_{0_{S_0}}, \dotsc P_{3_{S_{|S| - 1}}}\}$
\item Project scores are totaled yielding $\{p_0, p_1, \dotsc p_{|S| - 1}\}$
\item $G(p)$ will map $p$ to $\{A > B > C > F\}$ such that
\begin{equation}
\forall i \forall j,  p_i\ge y_j \implies G(p_i)\ge G(y_j) \nonumber \linebreak
\end{equation}
but:
\begin{equation}
\forall i \forall j,  p_i\gg y_j \centernot\implies G(p_i)\ge G(y_j) \nonumber
\end{equation}
and:
\begin{equation}
\forall i,  G(p_i) = \{A, F\} \implies S_i\ \text{really deserved it}\nonumber
\end{equation}
with approximate expectations:
\begin{equation}
|G_F| < |G_A| < \frac{|G_B|}{e} \simeq \frac{|G_C|}{e} \nonumber
\end{equation}
\end{itemize}
\end{frame}

\end{document}
